The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-04-03 main.tex
Update main.tex
Updated citation for this repository at the request of the journal editor

We start by describing the way the \astropy Project functions and is organized
in \sectionname~\ref{sec:org}. We then describe the main software efforts
developed by the \astropy Project itself: a core package called \astropypkg
(\sectionname~\ref{sec:core}) and several separate packages that help maintain
the infrastructure for testing and documentation
(\sectionname~\ref{sec:infrastructure}). We end with a short vision for
the future of \astropy and astronomical software in general in
\sectionname~\ref{sec:future}. The full paper, including the code
to produce the figures, is available in a \github
repository\footnote{\url{https://github.com/astropy/astropy-v2.0-paper}}

>>>>

We start by describing the way the \astropy Project functions and is organized
in \sectionname~\ref{sec:org}. We then describe the main software efforts
developed by the \astropy Project itself: a core package called \astropypkg
(\sectionname~\ref{sec:core}) and several separate packages that help maintain
the infrastructure for testing and documentation
(\sectionname~\ref{sec:infrastructure}). We end with a short vision for
the future of \astropy and astronomical software in general in
\sectionname~\ref{sec:future}. The full paper, including the code
to produce the figures, is available in a \github
repository \citep[][]{adrian_price_whelan_2018_1211397}\footnote{Codebase: \url{https://github.com/astropy/astropy-v2.0-paper}}.
